The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-06 Fsing/FThresholdsPaper/FThresholds.tex

\newpage
\section{Future work}

We conclude this note with some comments on possible future improvements to the package.

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.
\item  Add functionality to handle non-principal ideals.  The theoretical foundation for this is the paper of Karl and Kevin \cite{SchwedeTuckerTestIdealsOfNonPrincipal}.
\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).  There is one tricky theoretical things, we don't know when this process would stop.  If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.  Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
\end{enumerate}

>>>>

\newpage
\section{Future Directions}

{\color{red} Should we add this section to the \textbf{Organization} part of the intro?}

We conclude with some comments on possible improvements to the package.

One natural candidate for improvement would be to extend functionality to better handle nonprincipal ideals.  In particular, the package could be improved if it could use the test ideals $\tau(I^t)$ when $I$ is not necessarily principal.  Fortunately, the theoretical foundation for computing such ideals has already largely been worked out in the paper \cite{SchwedeTuckerTestIdealsOfNonPrincipal}. However, such an improvement would necessarily require an update to the \emph{TestIdeals} package.

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

\item Extend binary forms functions to handle more general $F$-thresholds (that is, with respect to diagonal ideals).  There is one tricky theoretical things, we don't know when this process would stop.  If we can do this, then we can compute $F$-pure thresholds of binary forms in non-standard gradings.  Cite the paper by Daniel and Pedro \cite{HernandezTeixeiraFThresholdFunctions}.
\end{enumerate}
